
---
title: "Week 7 Workshop"
author: "Katie Miller"
date: "`r Sys.Date()`"
output: word_document
execute: 
warning: FALSE
---

```{r message = FALSE}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

# Linear Models
How does stem length _predict_ stem dry mass?

```{r filtering-data}
maples_data <- hbr_maples %>% 
  filter(year == 2003 & watershed == "Reference")

```

Visualize missing data

```{r missing-data-vis}
gg_miss_var(maples_data)
```


Exploratory data visualization 

```{r}
ggplot(data = maples_data, aes(x= stem_length, y = stem_dry_mass)) +
       geom_point()
```

Let's try a model

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length,
                   data = maples_data)

maples_model
```

Check assumptions

I. linear relationship: yes! Plot in console 
II. independence of errors: yes! (based on data collection)
III. Homoskedasicity of errors: yes! (residuals vs. fitted plot)
IV. Normally distrobuted errors: yes! (QQ plot of residuals)

```{r checking-assumptions}
par(mfrow = c(2, 2))
plot(maples_model)
```


turn off 2 x 2 grid

```{r turn-off-grid}
dev.off()
```


# Putting together to communicate
## model predictions

```{r pulling-out-predictions}
prediction <- ggpredict(maples_model, terms = "stem_length")
```

plot predictions 

```{r}
plot_prediction <- ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) +
  geom_point() +
  geom_line(data = prediction, aes(x = x, y = predicted), color = "blue", linewidth = 1) +
  #confidence interval
  geom_ribbon(data = prediction, aes(x=x, y = predicted, ymin = conf.low, ymax = conf.high), alpha = 0.2)

plot_prediction
# same as previous plot 
```

# Create tables

```{r model-summary-tables}
model_summary <- summary(maples_model)

model_squares <- anova(maples_model)
```

making a table

```{r}
model_squares_table <- tidy(model_squares) %>% 
  # round the sum of squares and mean squares columns to have 5 digits (could be less)
  mutate(across(sumsq:meansq, ~ round(.x, digits = 5))) %>% 
  # round the F-statistic to have 1 digit
  mutate(statistic = round(statistic, digits = 1)) %>% 
  # replace the very very very small p value with < 0.001
  mutate(p.value = case_when(
    p.value < 0.001 ~ "< 0.001"
  )) %>% 
  # rename the stem_length cell to be meaningful
  mutate(term = case_when(
    term == "stem_length" ~ "Stem length (mm)",
    TRUE ~ term
  )) %>% 
  # make the data frame a flextable object
  flextable() %>% 
  # change the header labels to be meaningful
  set_header_labels(df = "Degrees of Freedom", 
                    sumsq = "Sum of squares",
                    meansq = "Mean squares",
                    statistic = "F-statistic",
                    p.value = "p-value")

model_squares_table
```

