
---
title: "Week 7 Workshop"
author: "Katie Miller"
date: "`r Sys.Date()`"
output: word_document
messages: false
---

```{r}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

# Linear Models
How does stem length _predict_ stem dry mass?

```{r filtering-data}
maples_data <- hbr_maples %>% 
  filter(year == 2003 & watershed == "Reference")

```

Visualize missing data

```{r missing-data-vis}
gg_miss_var(maples_data)
```


Exploratory data visualization 

```{r}
ggplot(data = maples_data, aes(x= stem_length, y = stem_dry_mass)) +
       geom_point()
```

Let's try a model

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length,
                   data = maples_data)

maples_model
```

Check assumptions

I. linear relationship: yes! Plot in console 
II. independence of errors: yes! (based on data collection)
III. Homoskedasicity of errors: yes! (residuals vs. fitted plot)
IV. Normally distrobuted errors: yes! (QQ plot of residuals)

```{r checking-assumptions}
par(mfrow = c(2, 2))
plot(maples_model)
```


turn off 2 x 2 grid

```{r turn-off-grid}
dev.off()
```




